A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2025-07-20 paper/restruct-new.tex
update

Looking at the dependencies in the reverse order, it is thus enough:
\begin{enumerate}
\item To assume frame$^{n-2,k}$ and painting$^{n-2,k}$ for all $k\leq
  p$ in order to mutually define, for all $p\leq n$, the type of
  restrframe$^{n-1,p}$ and frame$^{n-1,p}$ as a function from all
  restrframe$^{n-1,k}$ for $k\leq p$. Using red for assumptions, this
  can be pictured as:
\begin{center}
\begin{tikzcd}
frame^{n-1,p}(\textcolor{red}{restrframe^{n-1,k<p}}) \arrow[d] \\
\textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
\textcolor{red}{frame^{n-2,k<p}} \\
\end{tikzcd}
\end{center}
\item To further assume restrframe$^{n-1,k}$ for all $k\leq p$ to get
  frame$^{n-2,p}$ for all $p<n$:
\begin{center}
\begin{tikzcd}
frame^{n-1,p} \arrow[d] \arrow[ddr]\\
\textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
\textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}
\end{center}

\item To rely on frame$^{n-2,k}$, painting$^{n-2,k}$ and
  restrframe$^{n-1,k}$ now for all $k > p$, as well as an inhabitant
  of $X_{n-2}$ of nuSet$^{=n-2}$ to define painting$^{n-1,p}$ for all
  $p \leq n$:
\begin{center}
\begin{tikzcd}
& & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
& & & frame^{n-1,p} \arrow[d] \arrow[ddr]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}
\end{center}

@@

\item To rely on frame$^{n-2,k\geq p}$, painting$^{n-1,k\geq p}$ and
  restrframe$^{n,k\geq p}$ to build frame$^{n,k\geq p}$ and
  painting$^{n,k\geq p}$ for $p \leq n$:

@@

\item To rely on restrpainting$^{n-1,k}$ and cohframe$^{n,k}$ for $k >
  p$ to also get restrpainting$^{n,p}$ for all $p \leq n$:

@@

\item To finally assume cohpainting$^{n,k}$ for $k \geq p$
to get cohpainting$^{n+1,p}$ for $p \leq n-1$:

>>>>

Looking at the dependencies in the reverse order, it is thus enough:
\begin{enumerate}
\item To assume frame$^{n-2,k}$ and painting$^{n-2,k}$ for all $k< p$
  in order to mutually define, for all $p\leq n$, the type of
  restrframe$^{n-1,p}$ and frame$^{n-1,p}$ as a function from all
  restrframe$^{n-1,k}$ for $k< p$. Using red for assumptions, this
  can be pictured as:
\begin{center}
\begin{tikzcd}
frame^{n-1,p}(\textcolor{red}{restrframe^{n-1,k<p}}) \arrow[d] \\
\textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
\textcolor{red}{frame^{n-2,k<p}} \\
\end{tikzcd}
\end{center}

\item To further assume restrframe$^{n-1,k}$ for all $k<p$ to get
  frame$^{n-1,p}$ for all $p\leq n-1$:
\begin{center}
\begin{tikzcd}
frame^{n-1,p} \arrow[d] \arrow[ddr]\\
\textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
\textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}
\end{center}

\item To rely on frame$^{n-2,k}$, painting$^{n-2,k}$ and
  restrframe$^{n-1,k}$, jointly with frame$^{n-1,k}$, and now for all
  $k \geq p$, as well as an inhabitant $X_{n-2}$ of $\nu$Set$^{=n-2}$
  to define painting$^{n-1,p}$ for all $p \leq n-1$:
\begin{center}
\begin{tikzcd}
& & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & & & frame^{n-1,p} \arrow[d] \arrow[ddr]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}
\end{center}

@@

\item To rely on frame$^{n-2,k\geq p}$, painting$^{n-2,k\geq p}$ and
  restrframe$^{n-1,k\geq p}$ to build frame$^{n-1,k\geq p}$ and
  painting$^{n-1,k\geq p}$ for $p \leq n$:

@@

\item To rely on restrpainting$^{n-1,k}$ and cohframe$^{n,k}$ for $k >
  p$ to also get restrpainting$^{n,p}$ for all $p \leq n-1$:

@@

\item To assume cohpainting$^{n+1,k}$ for $k \geq p$ to build
  cohframe$^{n+1,k\geq p}$:

\item To rely on restrpainting$^{n,k}$ and cohframe$^{n+1,k}$ for $k \geq
  p$ to also get restrpainting$^{n+1,p}$ for all $p \leq n$:

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{scriptsize}
\begin{tikzcd}
& & & frame^{n+1,p} \arrow[d] \arrow[ddr] \\
& & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
& & & frame^{n,p} \arrow[d] \arrow[ddr] & restrframe^{n+1,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & &
  painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] & restrpainting^{n,k<p} \arrow[d, dotted] \arrow[ddlll] \arrow[dddll] \arrow[l, dotted] \arrow[uul, dotted]\\
frame^{n-1,k\geq p} \arrow[d] \arrow[ddr] & restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & &
 frame^{n-1,p} \arrow[d] \arrow[ddr] & restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
   cohframe^{n+1,p} \arrow[d] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] &
   \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] &
   \textcolor{red}{cohpainting^{n,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] &
   \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
   \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted] &
   \textcolor{red}{cohpainting^{n,k<p}} \arrow[l, dotted] \arrow[d, dotted] \\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
   \textcolor{red}{frame^{n-2,k<p}} &
   \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
   \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
\end{tikzcd}
\end{scriptsize}

\item To finally rely on cohpainting$^{n,k}$ for $k \geq p$
to also get cohpainting$^{n+1,p}$ for $p \leq n-1$:
